Supplementary Material

### 2020-01-30 Figures.Rmd
omitted personal identifying information for double-blind peer review at Am Nat

---
output:
  pdf_document:
    keep_tex: true
    toc: false
    number_sections: false
    df_print: paged
    fig_caption: true
    citation_package: natbib 
header-includes:
  - \usepackage{fullpage}
  - \linespread{1.5} 
  - \usepackage{lineno}
  - \usepackage{caption,setspace}
  - \captionsetup[figure]{font=small}
bibliography: ReferencesAbbrev
biblio-style: EcolLett
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
linkcolor: black
urlcolor: black
citecolor: black
---

<!-- Begin title page formatting -->

\vspace*{0.1cm} 
\begin{center} \LARGE Ecological character displacement destabilizes food webs \end{center}

\bigskip

\begin{center} \large Matthew A. Barbour$^{1,2,\ast}$ \normalsize \end{center}

\bigskip

\noindent 1. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;

\noindent 2. University of British Columbia, Department of Zoology, 2212 Main Mall, Vancouver, BC V6T 1Z4, Canada;

$^\ast$ Corresponding author; e-mail: matthew.barbour@ieu.uzh.ch, phone: +41 44 635 61 63

\bigskip

*Statement of authorship*: MAB conceived the study, derived analytical solutions, performed simulations, and wrote the paper.

\bigskip

*Data accessibility*: No new data were used. All code used to reproduce this manuscript and simulations within are publically available on GitHub (https://github.com/mabarbour/ECD_model) and has been archived with Zenodo (https://zenodo.org/badge/latestdoi/79349192).

\bigskip

*Running title*: Character displacement destabilizes food webs

\bigskip

*Keywords*: competition; eco-evolutionary dynamics; consumer-resource interactions; adaptation; community stability

<!-- Remove rest of title page for bioRxiv submission-->
\bigskip

*Manuscript type*: Letter.

\bigskip

*Number of words in abstract*: 143; 
*Number of words in main text*: `r wordcountaddin:::word_count("manuscript_ECD_model.Rmd") - 143`;
*Number of words in text boxes*: NA;
*Number of references*: 45;
*Number of figures*: 4;
*Number of tables*: 0;
*Number of text boxes*: 0

<!-- End title page formatting -->

\linenumbers{}
\modulolinenumbers[3]

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)

## Load required libraries
library(deSolve) # numerical integration library
library(rootSolve) # for runsteady integration function
library(pse) # for latin hypercube
library(plyr) # for ldply
library(dplyr) # for manipulating data
library(tidyr) # for tidying data
library(cowplot) # for better base, ggplot graphics

## color palette
cbPalette <- c("#D55E00", "#0072B2", "#009E73")
```

```{r Simulations, include=FALSE, messages=TRUE, cache=TRUE}

#### GET REQUIRED FUNCTIONS ####

source('identify_steady_state.R')
source('eco_evo_sim_function.R')
source('Consumer_Resource_Functions.R')
source('CR_dynamics.R')

#### GENERAL PARAMETERS AND STATE VARIABLES ####

## Intrinsic growth rates
r <- 1
r1 <- r 
r2 <- r

## Carrying capacity
K <- 4
K1 <- K
K2 <- K

## Conversion efficiency
e <- 0.8
e11 <- e 
e12 <- e 
e21 <- e 
e22 <- e

## Mortality rate
m <- 1
m1 <- m
m2 <- m

## General, non-evolving parameter set for 2C,2R model
general_parameters <- data.frame(r1 = r1, r2 = r2, K1 = K1, K2 = K2, e11 = e11, e12 = e12, e21 = e21, e22 = e22, m1 = m1, m2 = m2)

## Attack rate
A <- 2
aii <- A*0.61

## Habitat preference (for LawlorSmith and McCann models)
w <- 0.6
wii <- w
wij <- (1 - w)

## Handling time (only for McCann model)
h <- 0.4
h11 <- h
h12 <- h
h21 <- h
h22 <- h

## State variables
R <- 2
R1 <- R
R2 <- R
C <- 1
C1 <- C
C2 <- C

states_2C_2R <- data.frame(R1 = R1, R2 = R2, C1 = C1, C2 = C2)
states_1C_2R <- data.frame(R1 = R1, R2 = R2, C1 = C1)

## Trade-offs. Borrowed from Sargent and Otto, 2006 Am Nat
a12_tradeoff <- expression(A*(1-(a11m/A)^n)^(1/n)) 
a21_tradeoff <- expression(A*(1-(a22m/A)^n)^(1/n))

n_concaveDN <- 1.15
n_linear <- 1
n_concaveUP <- 0.85

concaveDN_df <- data.frame(n = n_concaveDN, aii = seq(0,A,0.01)) %>% mutate(aij = A*(1-(aii/A)^n_concaveDN)^(1/n_concaveDN))
linear_df <- data.frame(n = n_linear, aii = seq(0,A,0.01)) %>% mutate(aij = A*(1-(aii/A)^n_linear)^(1/n_linear))
concaveUP_df <- data.frame(n = n_concaveUP, aii = seq(0,A,0.01)) %>% mutate(aij = A*(1-(aii/A)^n_concaveUP)^(1/n_concaveUP))

bind_rows(concaveDN_df, linear_df, concaveUP_df) %>%
  ggplot(., aes(x=aii, y=aij, color = factor(n))) + geom_line() + ggtitle("Attack rate trade-offs")

bind_rows(concaveDN_df, linear_df, concaveUP_df) %>%
  ggplot(., aes(x=aii/(aii+aij), y=aii+aij, color = factor(n))) + geom_line() + ggtitle("Relationship between specialization and total attack rate")

######################################### MACARTHUR MODEL #######################################################

## Mutant growth rates
mC1_MacArthur <- expression(e11*a11m*R1 + e12*a12m*R2 - m1)
mC2_MacArthur <- expression(e21*a21m*R1 + e22*a22m*R2 - m2)

#### PARAMETERS ####

## Linear
params_2C_2R_MacArthur_linear <- data.frame(general_parameters,
                                            a11 = aii, 
                                            a12 = eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_linear)),                     
                                            a21 = eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_linear)), 
                                            a22 = aii)                      
params_1C_2R_MacArthur_linear <- params_2C_2R_MacArthur_linear[c("r1","r2","K1","K2","e11","e12","a11","a12","m1")]

## concaveDN
params_2C_2R_MacArthur_concaveDN <- params_2C_2R_MacArthur_linear
params_2C_2R_MacArthur_concaveDN["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveDN))
params_2C_2R_MacArthur_concaveDN["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveDN))
params_1C_2R_MacArthur_concaveDN <- params_2C_2R_MacArthur_concaveDN[c("r1","r2","K1","K2","e11","e12","a11","a12","m1")]

## concaveUP
params_2C_2R_MacArthur_concaveUP <- params_2C_2R_MacArthur_linear
params_2C_2R_MacArthur_concaveUP["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveUP))
params_2C_2R_MacArthur_concaveUP["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveUP))
params_1C_2R_MacArthur_concaveUP <- params_2C_2R_MacArthur_concaveUP[c("r1","r2","K1","K2","e11","e12","a11","a12","m1")]

#### SIMULATIONS ####

## Linear
sim_2C_2R_MacArthur_linear <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_linear, 
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_MacArthur_linear <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_linear, 
                                init_states = states_1C_2R, 
                                eco_CR_model = MacArthur_1C_2R, 
                                AD_CR_models = c(mC1_MacArthur),
                                species_traits = c(1), 
                                eco_param_names = c("a11"), 
                                eco_tradeoff_names = c("a12"),  
                                evo_param_names = c("a11m"),  
                                evo_tradeoff_names = c("a12m"), 
                                tradeoff_functions = c(a12_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))
# asymmetric starting points
params_2C_2R_MacArthur_linear_asymm <- params_2C_2R_MacArthur_linear
params_2C_2R_MacArthur_linear_asymm[c("a21","a22")] <- sim_1C_2R_MacArthur_linear[nrow(sim_1C_2R_MacArthur_linear), c("a12","a11")] # replace C2's attack rates with the ending point of the C1 generalist simulation. This will create an asymmetry in the attack rates and follows the logic (and our results) that a likely scenerio with asymmetry is a specialist invading a generalist.
# just altering the parameters, everything else stays the same
sim_2C_2R_MacArthur_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

## concaveDN
sim_2C_2R_MacArthur_concaveDN <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveDN, 
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))
sim_1C_2R_MacArthur_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_concaveDN, 
                                init_states = states_1C_2R, 
                                eco_CR_model = MacArthur_1C_2R, 
                                AD_CR_models = c(mC1_MacArthur),
                                species_traits = c(1), 
                                eco_param_names = c("a11"), 
                                eco_tradeoff_names = c("a12"),  
                                evo_param_names = c("a11m"),  
                                evo_tradeoff_names = c("a12m"), 
                                tradeoff_functions = c(a12_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))
# asymmetric starting points
params_2C_2R_MacArthur_concaveDN_asymm <- params_2C_2R_MacArthur_concaveDN
params_2C_2R_MacArthur_concaveDN_asymm[c("a21","a22")] <- sim_1C_2R_MacArthur_concaveDN[nrow(sim_1C_2R_MacArthur_concaveDN), c("a12","a11")] 
sim_2C_2R_MacArthur_concaveDN_asymm <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveDN_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))

## concaveUP
sim_2C_2R_MacArthur_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveUP, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = MacArthur_2C_2R, 
                                       AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_MacArthur_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_concaveUP, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = MacArthur_1C_2R, 
                                       AD_CR_models = c(mC1_MacArthur),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveUP))
# asymmetric starting points
params_2C_2R_MacArthur_concaveUP_asymm <- params_2C_2R_MacArthur_concaveUP
params_2C_2R_MacArthur_concaveUP_asymm[c("a21","a22")] <- sim_1C_2R_MacArthur_concaveUP[nrow(sim_1C_2R_MacArthur_concaveUP), c("a12","a11")]
# max iterations reached!
sim_2C_2R_MacArthur_concaveUP_asymm <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveUP_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveUP))

######################################### LAWLOR SMITH COARSE-GRAIN MODEL #######################################################

## Mutant growth rates
mC1_LawlorSmith <- expression(e11*w11*a11m*R1 + e12*w12*a12m*R2 - m1)
mC2_LawlorSmith <- expression(e21*w21*a21m*R1 + e22*w22*a22m*R2 - m2)

#### PARAMETERS ####

## Linear
params_2C_2R_LawlorSmith_linear <- data.frame(general_parameters,
                                              a11 = aii,
                                              a12 = eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_linear)), 
                                              a21 = eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_linear)), 
                                              a22 = aii,
                                              w11 = wii, 
                                              w12 = wij, 
                                              w21 = wij,
                                              w22 = wii)
params_1C_2R_LawlorSmith_linear <- params_2C_2R_LawlorSmith_linear[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22")]

## concaveDN
params_2C_2R_LawlorSmith_concaveDN <- params_2C_2R_LawlorSmith_linear
params_2C_2R_LawlorSmith_concaveDN["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveDN))
params_2C_2R_LawlorSmith_concaveDN["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveDN))
params_1C_2R_LawlorSmith_concaveDN <- params_2C_2R_LawlorSmith_concaveDN[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22")]

## concaveUP
params_2C_2R_LawlorSmith_concaveUP <- params_2C_2R_LawlorSmith_linear
params_2C_2R_LawlorSmith_concaveUP["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveUP))
params_2C_2R_LawlorSmith_concaveUP["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveUP))
params_1C_2R_LawlorSmith_concaveUP <- params_2C_2R_LawlorSmith_concaveUP[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22")]

#### SIMULATIONS ####

## Linear
sim_2C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = LawlorSmith_2C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_linear, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
# asymmetric starting points
params_2C_2R_LawlorSmith_linear_asymm <- params_2C_2R_LawlorSmith_linear
params_2C_2R_LawlorSmith_linear_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_linear[nrow(sim_1C_2R_LawlorSmith_linear), c("a12","a11")] 
sim_2C_2R_LawlorSmith_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

## concaveDN
# max mut iter reach!
sim_2C_2R_LawlorSmith_concaveDN <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveDN, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = LawlorSmith_2C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveDN))
# note that although the max mutation iterations are reached, the evolving parameters appear to oscillate near high values, i.e. they are effectively at an ESS
plot(sim_2C_2R_LawlorSmith_concaveDN[,c("a11","a22")]) 
plot(sim_2C_2R_LawlorSmith_concaveDN[,c("a11","a22")], xlim=c(1.85,1.95))

sim_1C_2R_LawlorSmith_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveDN, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveDN))
# asymmetric starting points
params_2C_2R_LawlorSmith_concaveDN_asymm <- params_2C_2R_LawlorSmith_concaveDN
params_2C_2R_LawlorSmith_concaveDN_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_concaveDN[nrow(sim_1C_2R_LawlorSmith_concaveDN), c("a12","a11")] 
sim_2C_2R_LawlorSmith_concaveDN_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveDN_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))

## concaveUP
sim_2C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_2C_2R, 
                                        eco_CR_model = LawlorSmith_2C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                        species_traits = c(1,2), 
                                        eco_param_names = c("a11","a22"), 
                                        eco_tradeoff_names = c("a12","a21"),  
                                        evo_param_names = c("a11m","a22m"),  
                                        evo_tradeoff_names = c("a12m","a21m"), 
                                        tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_1C_2R, 
                                        eco_CR_model = LawlorSmith_1C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith),
                                        species_traits = c(1), 
                                        eco_param_names = c("a11"), 
                                        eco_tradeoff_names = c("a12"),  
                                        evo_param_names = c("a11m"),  
                                        evo_tradeoff_names = c("a12m"), 
                                        tradeoff_functions = c(a12_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
# asymmetric starting points
params_2C_2R_LawlorSmith_concaveUP_asymm <- params_2C_2R_LawlorSmith_concaveUP
params_2C_2R_LawlorSmith_concaveUP_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_concaveUP[nrow(sim_1C_2R_LawlorSmith_concaveUP), c("a12","a11")] 
sim_2C_2R_LawlorSmith_concaveUP_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveUP))

######################################### MCCANN MODEL #######################################################

## Mutant growth rates
mC1_McCann <- expression(e11*(((w11 * R1)/(w11 * R1 + w12 * R2)) * a11m * R1)/(1 + ((w11 * R1)/(w11 * R1 + w12 * R2)) * a11m * h11 * R1 + ((w12 * R2)/(w11 * R1 + w12 * R2)) * a12m * h12 * R2) + e12*(((w12 * R2)/(w11 * R1 + w12 * R2)) * a12m * R2)/(1 + ((w11 * R1)/(w11 * R1 + w12 * R2)) * a11m * h11 * R1 + ((w12 * R2)/(w11 * R1 + w12 * R2)) * a12m * h12 * R2) - m1)
mC2_McCann <- expression(e21*(((w21 * R1)/(w21 * R1 + w22 * R2)) * a21m * R1)/(1 + ((w21 * R1)/(w21 * R1 + w22 * R2)) * a21m * h21 * R1 + ((w22 * R2)/(w21 * R1 + w22 * R2)) * a22m * h22 * R2) + e22*(((w22 * R2)/(w21 * R1 + w22 * R2)) * a22m * R2)/(1 + ((w21 * R1)/(w21 * R1 + w22 * R2)) * a21m * h21 * R1 + ((w22 * R2)/(w21 * R1 + w22 * R2)) * a22m * h22 * R2) - m2)

#### PARAMETERS ####

## Linear
params_2C_2R_McCann_linear <- data.frame(general_parameters,
                                         a11 = aii,
                                         a12 = eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_linear)), 
                                         a21 = eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_linear)), 
                                         a22 = aii,
                                         w11 = wii, 
                                         w12 = wij, 
                                         w21 = wij,
                                         w22 = wii,
                                         h11 = h11,
                                         h12 = h12,
                                         h21 = h21,
                                         h22 = h22)

params_1C_2R_McCann_linear <- params_2C_2R_McCann_linear[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22","h11","h12","h21","h22")]

## concaveDN
params_2C_2R_McCann_concaveDN <- params_2C_2R_McCann_linear
params_2C_2R_McCann_concaveDN["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveDN))
params_2C_2R_McCann_concaveDN["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveDN))
params_1C_2R_McCann_concaveDN <- params_2C_2R_McCann_concaveDN[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22","h11","h12","h21","h22")]

## concaveUP
params_2C_2R_McCann_concaveUP <- params_2C_2R_McCann_linear
params_2C_2R_McCann_concaveUP["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveUP))
params_2C_2R_McCann_concaveUP["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveUP))
params_1C_2R_McCann_concaveUP <- params_2C_2R_McCann_concaveUP[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22","h11","h12","h21","h22")]

#### SIMULATIONS ####

## Linear
sim_2C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear, 
                                         init_states = states_2C_2R, 
                                         eco_CR_model = McCann_2C_2R, 
                                         AD_CR_models = c(mC1_McCann, mC2_McCann),
                                         species_traits = c(1,2), 
                                         eco_param_names = c("a11","a22"), 
                                         eco_tradeoff_names = c("a12","a21"),  
                                         evo_param_names = c("a11m","a22m"),  
                                         evo_tradeoff_names = c("a12m","a21m"), 
                                         tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_1C_2R_McCann_linear, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
# I'm thinking these initial asymmetric simulations don't quite make sense (at least for LawlorSmith and McCann). This is because I didn't switch the pre-adapted habitat preferences as well...This is important because C1 in the first simulation becomes C2 in the 2C-2R sim. This isn't an issue in the symmetry model, because I assume they are pre-adapted on different resources. 
# asymmetric starting points
params_2C_2R_McCann_linear_asymm <- params_2C_2R_McCann_linear
params_2C_2R_McCann_linear_asymm[c("a21","a22")] <- sim_1C_2R_McCann_linear[nrow(sim_1C_2R_McCann_linear), c("a12","a11")] # make sure a_ij and a_ii are in correct order. Note that habitat preference (w) is already set in the appropriate direction 
sim_2C_2R_McCann_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = McCann_2C_2R, 
                                AD_CR_models = c(mC1_McCann, mC2_McCann),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

>>>>

---
output: 
    pdf_document:
      keep_tex: true
      fig_caption: true
fontsize: 11pt
fontfamily: mathpazo
documentclass: article
header-includes:
  - \usepackage{fullpage}
  - \linespread{1.5} 
  #- \usepackage{lineno}
  - \usepackage{caption} # ,setspace
  - \captionsetup[figure]{font=small}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r foraging_scenarios, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:foraging_scenarios}**Ecological foraging scenarios.** I examined whether the effect of ecological character displacement on food-web dynamics depended on whether consumers competed for resources that occurred in the same (a) vs. different habitats (b). Note that inferences about character displacement can only be made by comparing food webs with (right) and without (left) a competing consumer, so I arbitrarily set *C*~2~ = 0 for these comparisons. The width of each arrow corresponds to the initial attack rate (*a*~ij~) of consumer *j* on resource *i*. Note that *C*~1~ was pre-adapted to *R*~1~ (*a*~11~ > *a*~21~), while *C*~2~ was a mirror image, being pre-adapted to *R~2~* (*a*~22~ = *a*~11~; *a*~12~ = *a*~21~). In each scenario, I assumed consumer feeding rates increased linearly with resource abundance. I also relax this assumption and consider a more realistic functional response when resources occurred in different habitats (b)."}
knitr::include_graphics("Fig_1_ForagingScenarios")
```

```{r tradeoff, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:tradeoff}**Evolutionary tradeoffs in consumer attack rates.** In each foraging scenario, I explored the effects of three different tradeoffs: intermediate combinations of attack rates (*a*~1,*j*~, *a*~2,*j*~) are higher than the extremes (green line, *n* > 1); extreme combinations of attack rates are higher than intermediate investments (orange line, *n* < 1); and all combinations of attack rates have the same total attack rate (blue line, *n* = 1). Points corresponding to attack rates at the beginning of the simulation for *C*~1~, which was pre-adapted to *R*~1~ (*a*~11~ > *a*~12~). Note that *C*~2~ was a mirror image of *C*~1~, being pre-adapted to *R*~2~ (*a*~22~ = *a*~11~; *a*~12~ = *a*~21~)."}
knitr::include_graphics("Fig_2_Tradeoffs.pdf")
```

```{r plot_fig3, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:plot_fig3}**Effect of character displacement on food-web dynamics under different evolutionary tradeoffs and foraging scenarios.** Lines show predicted values when both consumers and resources are present. Different line colors correspond to different tradeoffs in attack rates (green, *n* = 1.15; blue, *n* = 1; orange, *n* = 0.85). Large circles (two consumers) and triangles (one consumer) correspond to the end points of the eco-evolutionary simulation for *C*~1~ (the choice to display *C*~1~ was arbitrary), whereas as small shapes correspond to the starting points (only in stability panels). In both foraging scenarios, feeding rates increase linearly with resource abundance, but the equation for the effective attack rate is different."}
knitr::include_graphics("Fig_3_MacArthur_LawlorSmith.pdf")
```

```{r bifur_plot, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:bifur_plot}**Character displacement creates an unstable food web**. Lines illustrate the effect of character displacement across the range of specialization for *C*~1~ (the choice to display *C*~1~ was arbitrary), while the points are the results of an eco-evolutionary simulation. Note that I increased the total investment in attack rates (*A* = 3.3) to create a scenario that could result in an unstable food web. Although I specified a linear tradeoff in attack rates for this simulation, different tradeoff shapes do not qualitatively alter these results (see Appendix S4, Fig. S1)."}
knitr::include_graphics("Fig_4_Bifurcation.pdf")
```
